Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-10 manuscript.tex
overleaf update

The communication signal on a spacecraft is generated by utilizing a Continuous Wave (CW) seed laser that is carved by a fast intensity modulator. The resulting low-power pulsed signal is then amplified by an Erbium Doped Fiber Amplifier (EDFA) to increase its transmission power to Earth. The majority of the power used by the spacecraft for communication scales with the number of optical pulses due to the EDFA.

In our experiment, the 20 GHz repetition rate was limited by the jitter of the Single-Photon Detectors (SNSPDs) that we intended to use. These detectors have a Full Width at Half Maximum (FW(1/100)M) jitter of approximately 50 ps. To ensure that the response function of the entire experiment had jitter of around 50 ps FW(1/100)M, we needed to build a Pulsed Phase Modulation (PPM) source with ultra-short optical pulses.

Carving a CW laser with our system would have introduced excessive timing uncertainty due to the limited ability of even the fastest lithium niobate intensity modulators to carve pulses with widths below 20 ps. The added jitter from modulated CW pulses, combined with the jitter of the detectors, would have exceeded the 20 GHz/50 ps slot width requirement.

>>>>

DSOC relies on modulation of a CW seed laser to generate the communication signal on the spacecraft. This signal is then amplified by an Erbium Doped Fiber Amplifier (EDFA) to increase its transmission power to Earth. As the EDFA amplifies the pre-generated pulses and uses most of the power of the spacecraft optical transmission system, power consumption scales with the number of optical pulses.

We produce our modulated singal by carving a series of mode locked laser pulses with lithium niobate modulators. This way, the jitter of the optical pulses themselves are not limited by the modulators or thew slew rate of the RF signal that drives them.
